% @brief    LaTeX2e Resume for Rohan Parikh
\documentclass[margin,line]{res}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Rohan Parikh}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    20 2nd St., APT 409			                            \hfill rohan.parikh21@gmail.com       \vspace{0mm}\\\vspace{0mm}%
    Jersey City, NJ 07302           						\hfill \vspace{0mm}\\\vspace{0mm}%       
    Mobile Number: (848)-228-0671					    	\hfill github.com/rohanparikh21  	  \vspace{0mm}\\\vspace{-4.5mm}%

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}
	\textbf{Rutgers University}, New Brunswick, New Jersey, USA. \hfill \textbf{2013--2015}\\
	%\vspace{0mm}\\\vspace{0mm}%
	\textnormal{Master of Science in Electrical and Computer Engineering (3.95/4)} \\
    \\
	\textbf{DA-IICT}, Gandhinagar, Gujarat, India. \hfill \textbf{2009--2013}\\
	%)\vspace{0mm}\\\vspace{0mm}%
	\textnormal{Bachelor of Technology in Information and Communication Technology (7.99/10)}
    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    \textbf{Bank of America Merrill Lynch}, New York, New York, USA \vspace{2mm}\\\vspace{1mm}%
    \textnormal{Technology Analyst} \hfill \textbf{Feb 2015 -- Present}
    \begin{description}
     \item[$\bullet$] Working as a developer in the Global Mortgages and Securitized Products group.
     \item[$\bullet$] Built a distributed pricing server by leveraging the grid infrastructure to calculate nominals and risk metrics from the position management application. Used the proprietary quant lib., Bloomberg and Intex as different pricing engines.
     \item[$\bullet$] Worked with Bloomberg API (BLPAPI) to feed in market data to various applications and spreadsheets used by the desk.
     \item[$\bullet$] Took initiative to leverage cashflow generation and Price/Yield calculation API provided by Intex to calculate risk metrics.
     \item[$\bullet$] Built an intraday alerting system for early detection and remediation of production issues.
	\end{description}

    \textbf{Bank of America Merrill Lynch}, New York, New York, USA \vspace{2mm}\\\vspace{1mm}%
    \textnormal{Technology Developer and Analyst Intern} \hfill \textbf{Jun 2014 -- Aug 2014}\\
    Developed modules to feed in data from external systems to the electronic trading application. 
    
    \textbf{Oracle India Pvt. Ltd.}, Bangalore, Karnataka, India \vspace{2mm}\\\vspace{1mm}%
    \textnormal{Intern} \hfill \textbf{Dec 2012 -- May 2013}\\
    Worked on a framework for test automation using Selenium WebDriver and HP Quick Test Professional for various Oracle Retail products.
    
    %__________________________________________________________________________________________________________________
    % Academic Projects
    \section{\mysidestyle Academic\\Projects}

    \textbf{Leveraging mobile/fixed cloud for object recognition}, CPS Lab, Rutgers University \vspace{2mm}\vspace{1mm}%
    \begin{description}
     \item[$\bullet$] Implemented K-SVD algorithm for an object recognition application in a mobile/fixed cloud infrastructure. The application sat on top of the Maestro framework developed by the CPS Lab.
     \item[$\bullet$] Used the All-Joyn framework developed by Qualcomm for the Android OS as a medium for peer-to-peer communication.
	\end{description}
    
    \textbf{Content based routing for small scale networks}, Rutgers University \vspace{2mm}\vspace{1mm}%
    \begin{description}
     \item[$\bullet$] Designed, developed and documented a protocol for content based routing. Documentation for the protocol had quality similar to RFC documents submitted to IETF.
     \item[$\bullet$] Delivery of a packet was based on name of the content being transferred as opposed to IP address as in traditional network. Implementation for this project was in C++.
	\end{description}
    
    \textbf{Search engine for Rutgers University (RU Search)}, Rutgers University \vspace{2mm}\vspace{1mm}\\
    Implemented a web crawler using tf-idf as a weighting factor. Leveraged hadoop for faster processing.
    
 %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Programming} 

    Python (Proficient), Java (Prior Experience), C++ (Learning), C (Prior Experience), Selenium, AMPS, KDB,
    Web frameworks, TCP/IP, TDD, Agile methodologies, version control (git, cvs).


%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF